An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
Now using faceted ternary plots for CD coefficients (without and with energy).

Figure~\ref{fig:CD_Scatter_Graph} shows a ternary plot 
of $\alpha$, $\beta$, and $\gamma$ parameter values 
for resample models for the Cobb-Douglas model (without energy).

<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters. $\\gamma$ is always 0.0, because energy is not included in this model.">>=
cdResampleTrianglePlot(energyType="none", facet_formula=~countryAbbrev )
@

@@

Figure~\ref{fig:CDq_Scatter_Graph} shows ternary plots 
for $\alpha$, $\beta$, and $\gamma$ parameter values 
for Cobb-Douglas (with energy) resample models.

<<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType="Q", facet_formula=~countryAbbrev)
@

Figure~\ref{fig:CD_GDP_Spaghetti_Graph} compares predictions 
from the Cobb-Douglas models 
(with and without energy) to historical data.

@@

The fit with lowest $sse$ of all the above trials is deemed the winner,
and its fitting parameters are used as the model.

>>>>

@@

% Figure~\ref{fig:CDq_Scatter_Graph} shows ternary plots 
% for $\alpha$, $\beta$, and $\gamma$ parameter values 
% for Cobb-Douglas (with energy) resample models.
% 
% Figure~\ref{fig:CD_Scatter_Graph} shows a ternary plot 
% of $\alpha$, $\beta$, and $\gamma$ parameter values 
% for resample models for the Cobb-Douglas model (without energy).

% <<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters. $\\gamma$ is always 0.0, because energy is not included in this model.">>=
% cdResampleTrianglePlot(energyType="none", facet_formula=~countryAbbrev )
% @
% 
% <<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
% cdResampleTrianglePlot(energyType="Q", facet_formula=~countryAbbrev)
% @

Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
for $\alpha$, $\beta$, and $\gamma$ parameter values 
for Cobb-Douglas (without and with energy) resample models.

<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without and with energy) resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevsForGraph, energyType="none")
  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
@

Figure~\ref{fig:CD_GDP_Spaghetti_Graph} compares predictions 
from the Cobb-Douglas models 
(without and with energy) to historical data.

@@

The fit with lowest $sse$ of all above trials is deemed the winner,
and its fitting parameters are used as the model.
